\section*{Week 50}
During this week we worked hard on finishing the report for Friday, many new
sections and major reconstructions have been performed on the report. The plan
is for everyone to read and comment on the report over the weekend, and finish
it next week. We also had our usability test during a social night, to make it
easier for the person to come by.

\subsection*{Reflection}
We are quiete happy with the progress this week, when it comes to editing then
there is always much reflectionon what could have been better. The usability
test were rushed quiete a bit, we had not entierly tested it on ourselves and
the computer running the system did not have an explanation text to a chapter we
asked her to find, resulting in her being very confused. However, there were
many situations where we could see she had issues, and some questions from her
about decisions. The output from the test was still great and many improvements
happends as a result of it, in the \autoref{cha:usability} describes the test
and what we lerned from it. The raw and premature test was properly not the best
experience from the users point of view, however, it would not be bad to make
the early test with another group. By doing this the flaws and biggest mmistakes
would be removed and hopefully provide a better experience fro the ``non
technical'' user.

\subsection*{Next Week}
During the next week, we plan to go through the notes on the report the group
members created over the weekend and apply fixes. Since the report would not get
anything new and the code is frozen, then there is no need for a weekly review.
