\section*{Week 38}
\subsection*{What Happend This Week}
This week we have researched further on Facebook, Twitter and articels about
how to sort and learn from user data on social media. We have furthered our
knowlegde on web crawlers and how we could use it this semester. In Web
Intelligence we have continiued on developing one, and it looks promishing for
our project. We have further evaluated on the tools we decided to use and how we
will be using them, we have decided to use a board and Trello to keep track of
task, with a different person in charge of keeping either uptodate. Every
morening we will have a short meeting about progress from yesterday and the days
task.

\subsection*{Evaluation}
We have found more information on what we can and can not do with social media,
and further our development on our web crawler. The report is getting some pages
as well, but there is not many gaps in our schedule for project work for now. We
have made some plans and furthered the groups structure and workflow for the
better.

\subsection*{Next Week}

``Insert picture''







During next week we would like to have a draft for the different researched
parts, from this week, ready for the report. Klaus also sent some links with
usefull information, this should also be read and notes on it. Moreover, we also
want to make a written description of the problem we would like to solve this
semester.





We edited the filter bubble and Facebook research parts of the report and continued work on the webcrawler. 
Finished research on the links from Klaus, and structured an idea for the final webagent.
Begun on the fundamental request builder to fetch information from Twitter.
