\section*{Week 40}
\subsection*{What Happend This Week}
This week we finished the initial problem and most of the analysis, which is
starting to be near a finishing point. We are now able to retrieve 3200 tweets
from each account a given user is following, meaning that if a user follows five
Twitter accounts then we will find 16000 assuming each account have 3200 tweets
or more.

We have spent some time thinking further upon how to use the vast amount of user
data, we are currently considering focusing on ``emotional wording'' such as
which hashtags and keywords go together, and if it is a positive or negative
tweet.

\subsection*{Reflection}
The application is progressing and we can gather user data now, however, we are
still working on improving the speed. We are not entirely sure about how to
handle the collected data, and we are still researching that. We are wondering
if we fulfil the requirements for the semester, and will discuss what we have
and expect to do and figure out if it is enough with our supervisor. It is
usually a requirement to bring along something from courses and which is
something we need to discuss as well. Our decision to meet at 9:00 is working,
and as a result, the project progress seems to be smoother.

\subsection*{Next Week} 
We will mainly perform edits and improve upon the code
next week because of a Programming Paradigms mini project. Therefore, we do not
expect much more progress.




% Mail
% Our Progress:
% Report: This week we have finished the following sections: Twitter Analysis,
% Initiating Problem and minor corrections (The acronyms in parentheses are marked
% because we haven’t added them properly yet).
% There are still sections in progress, not yet in the master.
% Code: We have managed to retrieve 3200 tweets for each account a given user is
% following. That is, if you follow "denmarkdotdk" and "VisitDenmark", we retrieve
% the 3200 most recent tweets from both of these accounts. We can store this data
% locally, and determine which words and hashtags in the tweets. Now we need to
% determine how we want to analyze the data, and the model we want to use to
% detect the "filter bubble". (We have mostly been talking about a neural network
% which attempts to classify the user's stance on a given subject by using words
% such as "stupid", "amazing", "idiot" etc.) Twitter seems like the best options
% from our current research.
% 
% The agenda for the meeting:
% - It's usually a requirement for us to bring something from our courses, how is
% it this semester? - Feedback

%  regarding the report: I only have minor comments, but rather a major comment
% outside the pdf: in the final report, there will be the scientific part and
% the reflection part (which is also scientific somehow .. ). However, it seems
% to me that in the report, there is also a sort of progress report included a
% bit, which won't be part of the final report. Let's talk about this tomorrow.
%  the code part: sounds exciting. Looking forward to hear more tomorrow.