\section*{Week 49}
This week we made many changes and edits to the report, the initial problem have
also been updated to better fit our current product, and the direction we ended
up taking. We have contacted a person studying politics at Aalborg University to
perform a user-test with since we won't be able to get a server up and running
with the solution, we will make the test next week.

\subsection*{Reflection}
The weekly reviews are starting to take up much space in the report because each
week is documented, it would probably have been better to make it a monthly
review instead. Going back and editing them sometimes leads to additions because
a task might have been finished in between weeks, or forgotten entirely. We are
not going to get our product tested on our American demographic
\autoref{sec:target}, we should have considered the distribution of our solution
earlier and examined what we have available at uni. It is part of a learning
experience, and we learned a lot from mistakes which is great.


\subsection*{Next Week}
We will perform the usability test of our system, we also have a goal of the
report being finished with all additions. Some commenting in the code still
needs to be done, however, no new features will be added. We are starting on the
major editing part and works towards finishing the report for Friday.



% Edits and updates on multiple chapters, initiating problem changed a little to better fit the the context.
% 
% Joanthan
% Fixed mistakes when extracting features, finished the data analysis chapter
% Restructured the analysis part to hopefully provide a better red thread for the reader.
% Began writing the implementation and accuracy testing of the Naive Bayes Implementation.
% 
% DonF
% Test the whole system in action (Not the result GUI screen). Fix some small errors in the code, such as locking the model such that it can be stored by one thread and does not cast the exception that the file is used by another process.
% Helped with collecting test data.
% 
% Mathias
% Made the GUI chapter
% Complete rework of the Worker chapter
% Made the Interaction with Twitter chapter
% A buttload of memes