\section*{Week 47}
\subsection*{What Happend This Week}
Not much have been done on the project this week, because of our Programming
and Paradigms delivery, however, the following have been done.
Work have been done on weekly summaries, they were not reflective enough which
have been fixed.
Our supervisor helped us setting up another meeting with the expert from week 43
\ref{Week43}, he will listen to what have happend since last and what we plan on
doing and give us feedback. The analysis algorithms have been improved and is
now 8 times faster.

\subsection*{Evaluation}
A major issue has been found when testing the Naive Bayes model. The model
currently predicts that everything belongs in the same category, this should
have been caught earlier perhaps by getting more stats from the test. 
%Kan ikke komme på mere men der burde være andet vi kan refkeltere på

\subsection*{Next Week}
Next week the summaries should be added properly to the report, and
documentation on the different parts of the application should be initiated. The
algorithm and Naive Bayes model should be functioning better and ready for use.


% There haven’t been one much on the project this week because of our Programming
% and Paradigms delivery, however, the following have been done.
% Work have been done on weekly summaries, they weren’t reflective enough which
% have been fixed.
% Our supervisor have also helped us getting a meeting with an expert on the
% field, who will listen to what we plan on doing and give us feedback.
% The analysis algorithms have been improved is is now 8 times faster.
% 
% 
% A major issue has been found when testing the Naive Bayes model. The model
% currently predicts that everything belongs in the same category. We have tried
% to make sure that there is an equal number of cases for each of the outputs,
% though that only changed the prediction to another category.
% 
% We have optimized the analysis algorithm, and improved its runtime by a factor
% of 8. We have also setup the worker such that it can be activated by a call to
% its API. We have also made it possible to post the result to the database
% server.
