\subsection{Facebook Analysis}\label{sec:facebook-analysis}
Facebook is a social media site with more than one billion users, each sharing
posts and personal details, and all of which are useful in the analysis and
detection of a person's \fbp. Facebook is used by both private citizens and
businesses to organise events, communicate, and share ideas.

\subsubsection{Using Facebook}
When using Facebook, most of the interaction with other users happens through
direct conversation with another user or through a page:

\begin{itemize}
  \item \textbf{User:} A user is a private citizen on Facebook. A user's
  ``feed'' is a core part used to continuously shows new posts from users and
  pages. Users can connect with other users via ``friendships'', which allows
  the user to see some of the posts on their feed.
  \item \textbf{Page:} A page can be used to either organise an event, a
  discussion forum or as a profile for a company. Users can mark these pages as
  ``liked'' which can be used both to get updates from the page and show
  others, what they like.
\end{itemize}


\subsubsection{Facebook API}
Facebook prohibits crawling/scraping of their website with a few exceptions such
as crawlers made by Google and Apple, whom still have a few restrictions to
follow \citep{FacebookRobotsTxt}. To access data on their site, they have
created the Facebook Graph \ac{API} as part of their developer platform, which
requires a registration of one's application, along with an accompanying
\ac{API} key used to perform queries. In addition to this requirement, there is
also a strict requirement of consent from the user of an application, which
needs to specify all the different types of data that the application wants to
access \citep{FacebookGraphApiAccessTokens, facebookPolicy}.\nl

An analysis of Facebook's Graph \ac{API} \citep{FacebookGraphApiDocumentation}
reveals that the platform previously allowed for more freedom when gathering
information about a user and their social activity on Facebook. However, this is
no longer the case as of version 2.0 of the \ac{API}
\citep{FacebookChangesInGraphTwoPointOh}.\nl

The current \ac{API} is limited to only listing those of the user's friends
that are using the same app and have given consent to let the app use their
details \citep{FacebookChangesInGraphTwoPointOh}. Access to the user's ``likes''
is limited to the interests listed on their profile, such as their favourite
movies and pages on Facebook, that they have marked as ``liked''
\citep{FacebookGraphApiUserEdges, FacebookGraphApiUserLikes}.

It is possible to access the user's posts and details regarding them, including
whether it originated from them or if another user shared it. These posts can
then be traced back one or more steps depending on the privacy settings of each
link in the ``share--chain'', but only limited information -- such as their
name and app-specific ID -- can be gathered about the users on the chain
\citep{FacebookGraphApiUserFeed}.\nl

To summarise, it is possible to use Facebook's \ac{API} to find connections
between existing users of the system. Knowledge of these users, based on what
the system has found out via other sources, can then be used to either confirm
or update the system's information on these individuals.