\subsection{Reddit Analysis}\label{sec:reddit-analysis}
Reddit is a social news aggregation and discussion website with over 250 million
users \citep{AdvertiseOnReddit}. The site is split into ``subreddits'' wherein
users can post entries as plain text, pictures and links to other websites.
Entries are ranked by the users who can either ``upvote'' or ``downvote''. This
is the case for both entries and comments \citep{AboutReddit}.\nl

% Users can follow other users such that all activity from the followed users is
% shown in a designated tab \fix{}{I mean like, yeah you can, but is it that
% relevant, not even a source}.

\subsubsection{Reddit API}\label{subsec:reddit-api}
Reddit has a \ac{REST} \ac{API} providing access to a user's information,
subscribed subreddits, posts and comments in subreddits. It also provides
moderators with a set of moderation tools that allow for manipulation of these
elements \citep{RedditApi}. Software that interacts with the \ac{API} must
follow certain rules.

These rules include using OAuth2 to ensure that a user has given consent and
that all requests are seen as coming from that user. This also requires checking
the rate-limiting headers returned with every server response and making sure
to not make too many requests.
Additionally, every client should provide a custom \ttt{User-Agent}
\ac{HTTP} header field, following the template: \citep{RedditApiRules}

\begin{center}
  \ttt{<platform>:<app ID>:<version string> (by /u/<reddit username>)}
\end{center}\nl
\begin{itemize}
  \item \ttt{platform:} a descriptive name for the platform type on which the
  client is running.
  \item \ttt{app ID:} a unique name for the client.
%\item[\ttt{app ID}] a unique name for the client, which could be formed like a
%Java package namespace.
  \item \ttt{version string:} identifies the version of the client uniquely
  within the given \ttt{app ID}.
  \item \ttt{reddit username:} is the username for the creator of a client who
  should be contacted by the Reddit team in case of problems.
\end{itemize}\nl

Spoofing another client or a browser using the \ttt{User-Agent} \ac{HTTP} header
field is strictly prohibited and results in a ban if discovered.
\citep{RedditApiRules}\nl

Based on the available information through the Reddit API, we should be able to
gather data about a user's comments and the subreddits they are subscribed to.
Based on our observations, many subreddits have distinct community cultures,
which often comes with an inherent political bias. As such, this information
should be sufficient for our analysis.
