\chapter{Discussion and Future Work}\label{fwork}
This chapter highlights different parts of the system which could
be improved for a future version of the application.

% \section*{Limit System}
% The limit on the amount of requests to Twitter we are allowed to make works fine
% on a small scale, as long as the user of the application does not use other
% programs that use requests from the same request pool as our application. This
% is due to the fact that our application does not check how many request there
% are remaining, which would risk exceeding the request limit. \nl
% %The limit rate system that exist in the program works on a small scale, when
% %only our application is used because we do not update the rate limits by
% %using a specific request or using the response from a
% %request.
% %The headers of a response contains the remaining request in the pool for that
% %category of requests. \nl 
% %Dette er erstattet af det over. Er du ikke er enig i ændringen siger du bare til :)
% 
% Before a potential release, a better implementation of limits would have to be
% made. This could be done by first sending a request to get the remaining amount
% of requests available and then each time a request is made using the response
% header, which contains the remaining amount of requests, to update the
% limits in the system.\nl


%For future use of the Twitter \ac{API} a better implementation for the limits
%system would be to make a request first to get the amount of requests the user
%has for each category, then each time a response is received from Twitter the
%header with the remaining amount of requests available. \nl

\section*{Queue API Authorisation}\label{disc:auth}
In the final version, the Queue API does not use any kind of authorisation for
the requests. This means that it is possible for anyone to send requests to the
queue server. The problem is that without authorisation, we cannot guarantee
that it is only our application that tries to analyse Twitter accounts. This
also means that our queue server needs to be robust enough to not crash when it
receives something that is not a proper request. \nl

While this is not a big problem for the current version of the application,
since it uses a local server, it would be a problem if the system were to be
released.

\section*{Word Updater for Bag-of-Words Implementation}
Right now, the Bag-of-Words classifier can only classify using already known
words which have been premade and stored in a list. This results in the
classifier being able to classify tweets with a high accuracy right now, but it
could, in a few months, lose some of that accuracy because of how the keywords
change. This is why we started to implement a system that should identify new
keywords and put them on a watch list using the Naive Bayes model. This
system has some functionality implemented, but it was not possible to complete
it within the time span.

For a system that should be able to be used without the maintenance required by
the Bag-of-Words classifier, the word updater should be developed in full. While
this approach is not perfect, it would allow us to dynamically update our model
in a shifting, political climate.
% A problem with the Bag-of-Words approach to determining the user's political
% leaning is that the model is unable to adjust itself or to react to a shifting
% political landscape. This is problematic, as some indicators of political
% affiliation, like names of current politicians, will likely change over time. In
% order to alleviate this problem, we have begun implementation of a system that
% will be able to identify patterns in keywords used by users.\\ 
% The general idea is that whenever the algorithm determines a clear political
% affiliation for a user, we can analyze that user to find more keywords which we
% can add to our keywords list. This would be done by finding uncommon words in
% the user's tweets' text. These words would then be added to a list of currently
% monitored words, and whenever a person with a clear political affiliation uses
% these words, we increment a counter for either left-wing or right-wing use of
% that word. Whenever we determine that we have enough data, we can add this word
% to our list of political keywords.\nl

%Outperform is single word :O http://www.thesaurus.com/browse/outperform
\section*{Using Additional Models}
The Naive Bayes and Bag-of-Words models are simplistic models. On other
data sets, they are outperformed by more advanced models, such as the Support
Vector Machine and Neural Networks. In the future, it would be interesting to
see how these models measure up to the ones, we currently use.

\section*{Larger training samples}
One of the problems with the Naive Bayes model is that the number of training
samples are limited to 120, with actual training only using 90. Under more ideal
circumstances, the training set should be increased by a factor of 10 or 100.
If using a sizable, varied and balanced training set, it should be possible to achieve a
better prediction rate at the cost of slower predictions. This can also be
extended to other models.\nl

By using larger training samples, there will be more features to consider, which
should increase accuracy a lot. But there will also be a larger requirement on
the memory usage. From what we experienced while working on Naive
Bayes, this can be quite a problem for other models. To work around
this, we will need to consider reducing the number of features we use. A
suggestion from \autoref{subsec:Exp2} was to use Principal Component Analysis.
This idea, along with other methods of reducing the dimensionality of the
features, would need to be explored further.

\section*{More Usability Evaluations}
It would be beneficial to perform more usability evaluations. The current
evaluation was performed with a single user, which is far from enough. In the
future, we should perform more evaluations with between 4-8 users. Using the
updated product, this should uncover the majority of the issues. The same set of
exercises can be used in the following tests as the purpose of the test has not
changed. It would also be beneficial to perform the tests with native English
speakers, as they are more familiar with terms such as sentiment and bias.\nl
 
In the future, it would be interesting to release a version and ask people on
social media sites to use it and provide feedback on how accurate they judge
the models to be. This would especially be helpful in judging how accurate our
current models are.

\section*{Result Page Person Identification}
Currently, we cannot identify who each person is in the filter bubble on the
result page. This would be a nice feature to have, as the user could be
curious about where specific people they follow are placed on the scale without
having to look each of them up individually. In addition to this feature, a
shortcut to looking up the filter bubble of another user could be added by
allowing the user to click on a specific user in their filter bubble.



\section*{Recommendation System}
In the initial design idea of the web application, the application listed
different Twitter accounts that would help the user's Twitter feed get closer to
the middle of the political spectrum, thus breaking their filter bubble. \nl

This feature would have to be developed before actual bubble busting would take
place. One way of implementing this feature would be to make a separate
database of recommended users with data generated from earlier searches. This
database would have to start out with some pre-analysed accounts.
Otherwise, the first few users of the program would not get any
recommendations. There would have to be a filter on which users are added to
the database. This could be a requirement of at least 10000 followers.
Otherwise, people would get irrelevant Twitter accounts recommended. If the
application had a lot of traffic, a filter on what kind of people they want to
be recommended could be implemented. For example, some people could prefer to
only get well-educated people recommended rather than celebrities who happen to
tweet politically a lot.\nl

Additionally, as we use \url{www.allsides.com} for determining the
political bias of news media sites, we could use this data to recommend news
media on the opposite side of the political spectrum.


\section*{Use Secure Communication Protocols}
Right now, all our \ac{API}s use HTTP. This could be a serious problem, as the
lack of encryption could allow a 3rd party to intercept the information
contained in our communications. While most of our data is freely available
through the Twitter API, it would be problematic when transferring the user's
authorisation information. This would be a major problem when releasing the
system, because the user should feel secure using our application with their
Twitter account.


\section*{Protecting Private Users}\label{sec:twitterProtect}
Some Twitter accounts are private, thus requiring the user to follow that
specific account before being able to access their tweets. Therefore, if a
private account was seached for and is in the database, it should not be
possible for a user which does not follow that account to view the results.
While this is not in violation with the Twitter API rules, it is bad practice.
While a boolean determining whether a Twitter account is private or not is stored in the
database, it is not currently used. This would have to be implemented before a
release.

\section*{Worker Unrecoverable Error}
If the worker encounters an error from which it cannot recover, it does not send
any information to either the Database Server or GUI Server. As such, a user
never receives the E-mail or any information. A common case would be if the user
tries to get the filter bubble of a private account they do not follow as this
would not return any information. Another case is if the user searches for an
account that does not exist. This is not acceptable in a finished system and
needs to be addressed before it can be released.

