\chapter{Usability Evaluation}\label{cha:usability}

To determine the quality of our graphical user interface, we have performed a
usability test. The usability test in this chapter is largely based
on \citep[p. 65-72 \& 269-275]{UXBook}, as it provides a well structured method
of performing usability evaluations.\nl

In \autoref{sec:UXTD}, we discuss how the test was designed and what the
purpose of each part of the test is. In \autoref{sec:UXUT}, we discuss the test
conditions and describe the events that occurred during the test.
Finally, in \autoref{sec:UXUR}, we rank the problems that the user encountered
in the test and provide solutions to these problems.

\section{Test Design}\label{sec:UXTD}
The test has been designed using a series of research questions as the basis
for two exercises. The goal of the exercises is to have the user use the
system in a simulated real world example. In addition to the test, we have two
questionnaires, one for the demographics and one for opinions.

\subsection{Research Questions}\label{subsec:UXRQ}
The research questions are used to guide the direction of the tasks, as well as
the analysis. We used the research questions on \citep[p. 70-71]{UXBook} as the
basis, with a focus on user interaction and understanding the information.
The following research questions are used as the basis for the tasks:

\begin{enumerate}
  \item \textbf{Web Sites:} 
	\begin{itemize}
      \item How easily do users understand what is clickable?
      \item How easily and successfully do users find the information
      explaining what they are looking at?
      \item How easily and successfully do users understand the authorisation
      steps for the site?
    \end{itemize}
  \item \textbf{Documentation:}
    \begin{itemize}
      \item How well do they understand the content of the topics they find?
    \end{itemize}
  \item \textbf{General:}
    \begin{itemize}
      \item What are the major usability flaws that prevent users from
      completing the most common tasks?
    \end{itemize}
\end{enumerate}

\subsection{Exercises}
Based on the research questions in \autoref{subsec:UXRQ}, we created the tasks
seen in \autoref{app:UXTasks}. There are two exercises, each trying to simulate
how a user would use the system.\nl

\subsubsection{Exercise 1}\label{subsub:UXE1}
The first exercise is divided into three tasks. The premise of the exercise is
that the user has not used the system before and has heard of it by
word-of-mouth.\nl

The first task requires the user to log into the system using a
pre-selected Twitter account. This tasks is used to see how well the user
responds to the steps necessary before the user can see his/her
bias.\nl

The second task requires the user to find his/her bias. This information is
shown several places and is intended to show that we have multiple methods of
determining the bias.\nl

The third task requires the user to locate the information that explains why
bias is shown multiple times. This task is present to see how well the information
is presented aFnd explained to the user.

\subsubsection{Exercise 2}
The second exercise is divided into two tasks. The premise of this exercise is
that the user, now more familiar with the system, wants to find the bias of a
friend.\nl

The first task requires the user to find the sentiment of a given user's
friends, those he/she is following. This task is in hindsight problematic as we
previously asked the user to log in to check their bias. By using the words log
in, in the test we might have planted the idea that it is not possible to use
other people's Twitter names to determine their bias. This is not the case, as
no code is required to request and see the bias of a Twitter user. The goal of this task
is to see how easily the user considers finding another person's bias using
their Twitter name.\nl

 The goal of the final task is to see how easily another user's information is
 found, it should also show if it is easier to find information when the user
 knows what to look for.


\section{Usability Test}\label{sec:UXUT}
The test is structured to proceed the following way: The user is given a
questionnaire to see how close he/she is to the target audience. The user is
then given a very brief overview of what the program does and asked to read the
exercises and make sure he/she understands them. The user then proceeds through
the exercises, as seen in \autoref{subsec:UXTest}. Finally, the user is given
another questionnaire which asks them to evaluate their experience.

\subsection{Test Conditions}
The usability test took place on the December 12th, 2017. Due to time
constraints, the test and evaluation are performed with a single user,
using a prototype with some of the interface's features not present. It is
decided that the test is to proceed regardless of the missing features as it is considered
necessary to get some outside feedback.\nl

The test is performed on a computer using real data, collected in real time. The
test is captured using a web camera for the user's expressions and voice, and
screen capture is used to track mouse movement. Present during the test is the
representative user, a test moderator and data logger. The test moderator
ensures that the user understands the task and helps if the user has been
stuck on a task for a lengthy amount of time. The data logger observes the test
and writes down observations and moments of interest for later analysis.

\subsection{The Test}\label{subsec:UXTest}
The test is conducted by a test moderator and a data logger. After the test was
completed, several key issues have become apparent with the execution of the
test. One of the main issues is that the test moderator and data logger are
inexperienced and ended talking with the test user too much, occasionally
trying to help her with suggestions after only minor issues. There is also the problem
of some missing features which were not properly taken into account when the
test was created. Though there were many problems, the outcome is still
relevant.

\subsubsection{Exercise 1 - Duration: 11 minutes}
The first exercise starts poorly as the user spends close to a minute on
the first screen trying to get started, only proceeding after finally receiving help.
The first issue the user encountered was that the way to proceed was
a link with no indication of being a link. After navigating to the
next page, the user proceeded to input the Twitter username and read what is
required in the verification process. She finds the link and proceeds to
a screen on Twitter's website which shows which permissions are
needed by the application. Here, she expresses that she would usually not allow
an application to do \textit{write} operations but would allow it this time for
the sake of the test. The rest of the task proceeds smoothly, though she looks
confused as to why the confirmation text is suddenly in the upper left corner.
She then proceeds to wait for the mail to arrive and makes small talk with the test
moderator.\nl

The second task starts when the E-mail with the result arrives after four
minutes of small talk. The user proceeds to look at the graphs and becomes
quiet. She then proceeds to look at the graphs in frustration for two minutes
while hovering over the bars. After finding one of the correct graphs, she
proceeds to the final task.\nl

The final task is problematic, as we, due to miscommunication, do not have any
information other than graph names and what type of model is used to create it.
The test user proceeds to look for the information above each of the graphs. The
test user then proceeds to scroll to the top of the page to see if there is a
description there. The task is ended shortly after.

\subsubsection{Exercise 2 - Duration: 7 minutes}
Exercise 2 begins with the user still looking at the graphs from the previous
exercise. The test user is told to find the sentiment of another user. She proceeds
to look at the Sentiment/Bias graph, a 2D graph where each user is a point. As
she finds no information about specific users from that she proceeds to look
around on the same page, until she asks for help about two minutes later. After
being asked to consider how she found her current information, she quickly
proceeds to the front page to verify what user she requested information about.
An issue is that she proceeds to click several times on the button, without
receiving a response. The rest of the task is quickly finished after she
receives the E-mail, the only problem is she has trouble connecting sentiment
with positivity/negativity. This is likely to be an issue with non-native
English speakers.\nl

In the final task, the test user proceeds to find one of the bias graphs
and quickly finds the bias of the other user.

\section{Usability Result}\label{sec:UXUR}
Based on the experiences and difficulties which we obtained during the test,
we have compiled a list of problems. The list has been rated using
\autoref{tab:UXCrit} from our \textit{Design and Evaluation of User Interfaces}
course.

\begin{table}[H]
\centering
\begin{tabular}{|l|l|l|l|}
\hline
 & Delay & \begin{tabular}[c]{@{}l@{}}Irritation/\\ irrationality\end{tabular}
 & \begin{tabular}[c]{@{}l@{}}Expectation\\ vs. actual\end{tabular} \\ \hline
Cosmetic & \textless 1 minute & Low & Small diff.\\\hline 
Serious & \begin{tabular}[c]{@{}l@{}}Several\\ minutes\end{tabular} & Medium & \begin{tabular}[c]{@{}l@{}}Significant\\ diff.\end{tabular} \\ \hline
Critical & \begin{tabular}[c]{@{}l@{}}Total\\ (User stops)\end{tabular} & Strong & Critical diff. \\ \hline
\end{tabular}
\caption{Guidelines for classifying usability problems.}
\label{tab:UXCrit}
\end{table}

The following problems were identified and rated:\nl

\textbf{Critical:}
\begin{itemize}
  \item Not enough explanations anywhere.
  \item When asking for permissions we ask to be allowed to send tweets on the
  users behalf.
\end{itemize}

\textbf{Serious:}
\begin{itemize}
  \item The \textit{Check Twitter user} button to begin at the front is
  difficult to find as it looks like text.
  \item There is too much information at once, when the graphs are shown.
  \item Expects to find information on friends in graphs or somewhere close.
\end{itemize}

\textbf{Cosmetic:}
\begin{itemize}
  \item Long waiting times before a reaction when clicking on the \textit{Check
  Twitter User} button on the start screen.
  \item Confirmation text is presented in the corner.
  \item Bars provide unexpected information.
  \item Nearly misses the small link on the \textit{Twitter Verification} page.
\end{itemize}

\section{Solutions}
Based on the results from \autoref{sec:UXUR}, we have the following suggestions
for improving the program and user experience. These have been aggregated under
the part of the program they pertain to:

\subsection*{Home Page} To fix the issue of the test user not being able to find
the \textit{Check Twitter User} button, the button should either look more like
a button or be replaced with the request page.

\subsection*{Authentication}
Since the test user had a minor problem finding the link to acquire the
authentication PIN, an actual button would solve this problem.\\
When asked to accept the permissions required by the application, she thought
they were too invasive. This can be fixed by reevaluating which permissions
are absolutely necessary.

\subsection*{Result Screen}
The test subject had no idea what any of the graphs meant and all the graphs
seemed overwhelming. To solve this, more information has to be
associated with each graph. For example, there was no way of knowing that the
green bar was where the user is located. 

\subsection*{Solutions to Overall Issues}
When waiting for the result to arrive, the test user said that there are way too
few explanations. This is fixed by adding information about each element
on each page. An information button could be added to the home page, explaining
all the overall ideas and concepts in the application.
