\section{Reflection on the Whole}\label{sec:FinRef}
The meeting with Dr. Stefan Schmid was surprising and we did
not really know what to expect but it turned out to be a very good experience. Not only
did we get many new ideas and suggestions for the project, our desire for the
solution was improved greatly as well. A meeting such as this is something we
would recommend and attempt to to in future projects as well.

Later in the project we had a few social night, these nights greatly improved
morale and meant we had more fun together. Since it was during the afternoon it
was time which was not usually spent on the project, a group member also had a
neighbour come down and test the system, which is easier to get when they live
nearby and are done for the day. Social nights such as these greatly benefits
morale and definitely helped with the groups workflow, and should be repeated. 

When someone performed some work in the group, and it was replaced or hugely
edited, it did not cause issues or a bad mood like it has in other groups.
Instead if there were issues they were discussed and a solution was quickly
found, also in cases where a section was removed entirely. 

We felt like the weekly reviews was pressed upon us, we see how it can be used
and it is important. But when the entire group had it at first semester it seems
like a repeat and a waste of time. The normal reflection done at the end of a
semester should be sufficient. Writing the reviews felt like a chore and a time
waste we had to do, and not much was gained from it since we already had
discussed the points highlighted there. What we had to do was remembering it and
writing it cleanly in the report for others.