\subsection{Week 44}
\subsubsection{What Happened This Week}
We have made an early model of the system. A lot of work has gone into
specifying how the different parts should interact with each other. Besides that
we have researched, tried to create and test a couple of different machine
learning models. We have also begun writing about sentiment analysis and how we
intent to analyse data.


\subsubsection{Reflection}
While we are happy with the direction of the project, we are somewhat suprised
at how easily we decided to make the project much more ambitious in scope. The
new direction has also meant that the workload has increased, which has meant
that we have not been able to work together on many of different subjects. It
has also had the unintended sideeffect that work on the report has slowed down
slightly. Instead it has forced us to become better at communication,
especially during the daily morning SCRUM meetings.\nl

We have talked with getting another meeting with Dr. Stefan Schmid on a later
date, as we feel it would be very beneficial to hear his thoughts once the
project is further along.

\subsubsection{Next Week} 
Next week we hope to have a better idea about how to classify tweets and
keep up with increasing workload.

% We made an early model of our neural network and wrote about sentiment
% analysis.
%  We setup the database and the API for the database and the authorazation for
% the API for the database, and an implementation part for it in the report 
% Queue server and REST API for queues server  Setup GUI using Laravel and
% started working on twitter authentication  and documentation in the report
% were started for the semester
