\subsection{Week 40}
\subsubsection{What Happened This Week}
We have finished writing most of the analysing, which is also starting to feel
finished. We have built a small program that can detect the political leanings
of hyperlinks using indexed list of american news web sites. We have considered
how to use ``emotional'' words, hashtags and positive/negative words as a way to
analyse the data.

\subsubsection{Reflection}
We are somewhat confused about some of the requirements for the study
regulation, as it has not been quite clear what exactly is meant ``internet
application, agent or service''. Does this include using an API to make
requests? We are also somewhat confused by what is required by the reflection
requirement. Per the suggestion of our supervisor we are going with this weekly
progress and reflection, which is why we are writing this. Our decision to meet
at 9.00 AM seems to have a positive influence on the project as it seems to
progressing smoother.

\subsubsection{Next Week} 
We have not planned a lot for next week as it is nearly scheduled full.



% Mail
% Our Progress:
% Report: This week we have finished the following sections: Twitter Analysis,
% Initiating Problem and minor corrections (The acronyms in parentheses are marked
% because we haven’t added them properly yet).
% There are still sections in progress, not yet in the master.
% Code: We have managed to retrieve 3200 tweets for each account a given user is
% following. That is, if you follow "denmarkdotdk" and "VisitDenmark", we retrieve
% the 3200 most recent tweets from both of these accounts. We can store this data
% locally, and determine which words and hashtags in the tweets. Now we need to
% determine how we want to analyze the data, and the model we want to use to
% detect the "filter bubble". (We have mostly been talking about a neural network
% which attempts to classify the user's stance on a given subject by using words
% such as "stupid", "amazing", "idiot" etc.) Twitter seems like the best options
% from our current research.
% 
% The agenda for the meeting:
% - It's usually a requirement for us to bring something from our courses, how is
% it this semester? - Feedback

%  regarding the report: I only have minor comments, but rather a major comment
% outside the pdf: in the final report, there will be the scientific part and
% the reflection part (which is also scientific somehow .. ). However, it seems
% to me that in the report, there is also a sort of progress report included a
% bit, which won't be part of the final report. Let's talk about this tomorrow.
%  the code part: sounds exciting. Looking forward to hear more tomorrow.