\chapter{Database \acs{API}}\label{DatabaseAPI}
After analysing a user, we want to store that data, such that we do not have to
retrieve or analyze the tweets again. As such, the system makes use of a
database, which the Workers can use to store and access the saved data. This
design choice is especially important, as we make use of the user's Twitter
account to retrieve data from the Twitter \ac{API}, which have a limited amount
of API requests, as described in \autoref{cha:twitterAPI}. As such, this section
is used to describe how we access and store this data, and how we make sure that
it is only accessible to authorized users.\nl

% In \autoref{sec:laravel} we start by describing the Laravel framework, which has
% been used to develop the front-end and the database \ac{API}. In
% \autoref{DBDesign} we continue by describing the design of our database and the
% data it is used to store. Then in \autoref{sec:APIDesign} we end by describing
% the implementation of the Database \ac{API}, and the different end-points we
% have defined for accessing data.

\section{Laravel Framework}\label{sec:laravel}
Laravel is a framework written in PHP that enables the creation of websites and
\ac{REST} web services, abstracting many underlying implementation details
including database access, user authentication and routing.\nl

Laravel's structure resembles that of the \ac{MVC} design pattern, with models
representing and managing database entities, views handling the presentation
layer without implementation logic, and controllers handling the main parts of
the logic. When needed, however, other types of layers can be added. This
includes helper classes and packages that extend the functionality of
Laravel.\nl

The main reason for choosing Laravel was group experience with various
frameworks and a preference for how Laravel does things.

\section{Database Design}\label{DBDesign}
While Laravel supports multiple \acp{DBS} \citep{LaravelDBS} we have opted to
use MySQL while developing and testing. Due to the use of Laravel's abstraction our
system should be able to run on any of the supported database systems without
any changes on our part.\nl

The system uses ten tables of which seven are used for authentication purposes
and one tracks database migrations. The remaining two tables are \textc{twitters}
and \\\textc{twitter\_twitter}, shown in part with example data in
\autoref{TwittersDBTable} and \autoref{TwitterTwitterDBTable} respectively.\nl

The columns \textc{created\_at} and \textc{updated\_at} have been left out here
due to size constraints on the pages.

\begin{table}[H]
\centering
\cc{
\resizebox{1.2\textwidth}{!}{%
\begin{tabular}{| l | l | l | l | l | l | l | l	| l | l |}
\hline
\textbf{\underline{id}} & \textbf{twitter\_name} & \textbf{twitter\_id} &
\textbf{analysis\_val} & \textbf{mi\_val} & \textbf{sentiment\_val} &
\textbf{media\_val} & \textbf{tweet\_count} & \textbf{protect} &
\textbf{processed} \\
\hline
\underline{224} & theDonaldDrumpf & 1234567 & 9.7323990 & 8.9295123 & -9.1618950
& -3.1275883 & 472 & 0 & 1 \\
\hline
\underline{225} & TayaDickinson & 914292 & 6.3012218 & 2.3406686 & -7.4462646 &
-6.2828786 & 414 & 0 & 0 \\
\hline
\underline{226} & BrodyHahn & 200519 & 1.9456733 & -7.2432034 & 4.1452475 &
-8.1468677 & 325 & 0 & 0 \\
\hline
\end{tabular}}
}
\caption{Table containing Twitter users and their determined values.}
\label{TwittersDBTable}
\end{table}

The table \textc{twitters} is used for storing data about analysed Twitter
users, such that we can reference this data if we should receive a request. This
allows reducing overhead, as we can reuse data. One important aspect is that we
need to respect a user's privacy. As such, we have introduced the ``protect''
boolean to indicate if only the Twitter user, which the result belong to, is
allowed to retrieve it. Although this is data in the database, this form of
protection is not implemented, details about this can be found in
\autoref{sec:twitterProtect}.\nl

The \textc{processed} column is used to distinguish between users who have been
fully analysed, along with all the users they follow, versus those who have been
processed as followed accounts. In the example data in \autoref{TwittersDBTable}
this distinction can be seen as ``theDonaldDrumpf'' is the only processed entry,
while ``TayaDickinson'' and ``BrodyHahn'' are analysed because they are followed
by ``theDonaldDrumpf''.


\begin{table}[H]
\centering
\begin{tabular}{| l | l |}
\hline
\textbf{\underline{twitter\_id}} & \textbf{\underline{follows\_id}} \\
\hline
\underline{224} & \underline{225} \\
\hline
\underline{224} & \underline{226} \\
\hline
\end{tabular}
\caption{Table that keeps track of followers.}
\label{TwitterTwitterDBTable}
\end{table}

The table \textc{twitter\_twitter} is used as a link table, named as
it is due to convention more so than any requirements from the framework. It keeps track
of the followers and in the example data it is shown how we keep track of the
users followed by ``theDonaldDrumpf''.

\section{\acs{API} Design}\label{sec:APIDesign}
To access the database described in \autoref{DBDesign}, we have
developed a \ac{REST} \ac{API} using Laravel. This
\ac{API} functions as a layer on top of the database, to which we can make
requests and retrieve data through the use of authorised \ac{HTTP} requests.

\subsection{\acs{API} Endpoints}
To enable external applications to interact with the \ac{API} we must
define a number of endpoints that covers the data and functions that can be
performed on it. These are based on the following base \ac{URL}:\nl

\say{http://localhost:8000/api/}\nl

In this example, the domain for the \ac{API} is localhost on port 8000, as this is
the default for locally hosted Laravel applications. If the application was to
be hosted somewhere, it would have a domain and would likely run on port 443,
just as the scheme would be \textc{https://}.\nl

The defined endpoints are described in \autoref{DBAPIEndpointTable}. It is worth
noting that \textc{boolean} is either \ttt{0} or \ttt{1}, so \ttt{true} and
\ttt{false} are not permitted as input. 

\begin{table}[H]
\centering
\begin{tabular}{| l | l | l |}
\hline
\textbf{METHOD} & \textbf{Endpoint} & \textbf{Required Data} \\
\hline
POST & /twitter                       &  \ttt{string} twitter\_name \\
~    & ~                              &  \ttt{int} twitter\_id \\
~    & ~                              &  \ttt{double} analysis\_val \\
~    & ~                              &  \ttt{double} mi\_val \\
~    & ~                              &  \ttt{double} media\_val \\
~    & ~                              &  \ttt{double} sentiment\_val \\
~    & ~                              &  \ttt{int} tweet\_count \\
~    & ~                              &  \ttt{boolean} protect \\
\hline
\multicolumn{3}{| l |}{\textit{%
Adds a single user's results to the database and returns the}} \\
\multicolumn{3}{| l |}{\textit{%
record ID of the created user, if creation was successful.}} \\
\multicolumn{3}{| l |}{} \\
\hline
PUT  & /twitter/add\_follower         &  \ttt{int} record\_id \\
~    & ~                              &  \ttt{int} follows\_id \\
\hline
\multicolumn{3}{| l |}{\textit{%
Creates link between two record IDs specifying that \ttt{record\_id}}} \\
\multicolumn{3}{| l |}{\textit{%
follows \ttt{follows\_id} on Twitter.}} \\
\multicolumn{3}{| l |}{} \\
\hline
PUT  & /twitter/finalize              &  \ttt{int} record\_id \\
~    & ~                              &  \ttt{string} request\_id \\
\hline
\multicolumn{3}{| l |}{\textit{%
Marks the user as processed and then forwards the \ttt{request\_id}}} \\
\multicolumn{3}{| l |}{\textit{%
to the \acs{GUI} server to notify it of the completion.}} \\
\multicolumn{3}{| l |}{} \\
\hline
GET  & /twitter/has/\{twitterName\}   &  \\
\hline
\multicolumn{3}{| l |}{\textit{%
Looks for a recent result for the given Twitter name.}} \\
\multicolumn{3}{| l |}{\textit{%
If found the record ID is returned.}} \\
\multicolumn{3}{| l |}{} \\
\hline
GET  & /twitter/has-id/\{twitterId\}  &  \\
\hline
\multicolumn{3}{| l |}{\textit{%
Looks for a recent result for for the given Twitter ID.}} \\
\multicolumn{3}{| l |}{\textit{%
If found the record ID is returned.}} \\
\multicolumn{3}{| l |}{} \\
\hline
GET  & /twitter/\{recordId\}          &  \\
\hline
\multicolumn{3}{| l |}{\textit{%
Returns the full result for the given record ID if it exists.}} \\
\hline
\end{tabular}
\caption{\ac{API} endpoints for the database back-end.}
\label{DBAPIEndpointTable}
\end{table}
 

\subsection{Authorization}
To make sure that data is only available to authorised users, we make
use of Laravel Passport, which is a token-based authorisation system based on
the OAuth2 standard \citep{LaravelPassport}.\nl

To make a request to the database, the user has to supply a token, which is an
encrypted string. This token is then verified by comparing it to a list of
active tokens on the database. The token verification is handled by Laravel
Passport.\nl

Of the multiple options that Laravel Passport provides for auth, we opted for
the one called ``client credentials'' which is meant for machine--to--machine
communication, as opposed to user--to--machine auth.
\citep{LaravelPassportClientCredentials}

The base \ac{URL} for auth requests is the same as for the \ac{API} except not
prefixed with \ttt{/api}.\nl

To retrieve a token, a worker must make a request to the
``oauth/token'' endpoint, while supplying a valid client ID and client
secret, along with the grant type, which will always be
``client\_credentials''. The request spec is documented in
\autoref{DBAPIOAuthEndpointTable}.\nl

If the supplied credentials are valid as per the information stored in the
database, the request responds with a long-lived token that uniquely identifies
the client, be it a worker or the \ac{GUI}. This token must then be sent in the
header of every request as a bearer token.\nl

\begin{table}[H]
\centering
\begin{tabular}{| l | l | l |}
\hline
\textbf{METHOD} & \textbf{Endpoint} & \textbf{Required Data} \\
\hline
POST & /oauth/token  & \ttt{string} grant\_type \\
~    & ~             & \ttt{int} client\_id \\
~    & ~             & \ttt{string} client\_secret \\
\hline
\end{tabular}
\caption{\ac{API} endpoints for authorisation.}
\label{DBAPIOAuthEndpointTable}
\end{table}


