\chapter{Twitter API Interaction}\label{cha:twitterAPI}
Following the decision to use Twitter as the source of data in
\autoref{sec:social-media-conclusion}, this chapter documents how we interact
with the Twitter API and how we handle the authorisation required to access
their data. When accessing data through the Twitter API, each requester has a
limited amount of requests, they can make within a 15 minute time span
\citep{twitterRateLimit}. As an example, retrieving batches of tweets is
limited to 900 requests if made on behalf of a user and 1500 requests if made on
behalf of an application \citep{twitterTimelineRateLimit}. This limit on
requests makes it impossible to upscale the system to service multiple users at
a time, if we make all requests on behalf of our application. We have chosen
that instead of making requests on behalf of our application, we instead ask the
user to authenticate their Twitter account with our system, so that we can make
requests on behalf of their user instead. However, Twitter enforces a different
set of authentication requirements when making requests from a user instead of
an application \citep{TwitterAPIAuth}. This chapter describes how we make
requests on behalf of a user.\nl

In \autoref{sec:OAuth}, we start by shortly describing how Twitter handles
authorisation of requests made by users. Following this, \autoref{sec:reqHead}
is used to describe the structure of the authorisation header, which is a
variable used to verify our identity and intent.
In \autoref{label:stringCreate}, we end by describing how to assemble all of the
necessary information into the final authorisation header.

\section{OAuth}\label{sec:OAuth}
Whenever a request is made on behalf of a user, Twitter requires that request to
conform with the OAuth 1.0 authorisation protocol \citep{OAuth1}. This protocol
requires the request to contain information about the following
\citep{TwitterAPIAuth}:

\begin{enumerate}
 	\item Which application is making the request.
	\item Which user the request is made on behalf of.
	\item Whether the user has granted the application authorisation to post on the
user’s behalf.
	\item Whether the request has been tampered with by a third party while in
	transit.
\end{enumerate}

For a request to contain this information, we must create a request
header, consisting of a number of encrypted key-value pairs. 

\section{Request Header}\label{sec:reqHead}
For an \ac{HTTP} request to be valid in the Twitter API, it has to
contain seven key-value pairs in the header \citep{TwitterAPIAuth}. These can
be seen below:

\begin{itemize}
  \item oauth\_consumer\_key
  \item oauth\_nonce
  \item oauth\_signature
  \item oauth\_signature\_method
  \item oauth\_timestamp
  \item oauth\_token
  \item oauth\_version
\end{itemize}

The values, and how to get them, is described in the following subsections.

\subsection*{Consumer key}
The consumer key is a unique token that identifies who makes the request.
This key is bound to the specific application. We can manually retrieve
it from the Twitter website \url{www.apps.twitter.com}.

\subsection*{Nonce}
The nonce is a unique token generated for each request. This way, it can be
determined if a request has been submitted multiple times. As there is no
mandatory approach to generating this key, we have chosen to base it on a
combination of the request type (POST/GET), a requester's name and a timestamp.

\subsection*{Signature}
The signature is used by Twitter to assure that the request has not been
modified after being sent. It works by encoding all information from the initial
request into a signature, and if this signature is not representative of the
request Twitter receives, it is considered invalid \citep[sec
3.4]{OAuth1}. In practice, we do the following \citep{TwitterAPISignature}:

\begin{enumerate}
  \item  Use percent-encoding to encode all the parameters, the
  request type and the key-value pairs.
  \item Concatenate all the encoded strings.
  \item Then concatenate the two additional values which identify the
  requesting user and the application, namely the \textc{OAuth token secret}
  and the \textc{Consumer secret}. Here the Token Secret is unique to the user
  and is given to us by Twitter when the user authenticates with our
  application. The \textc{Consumer Secret} is a unique identifier for our
  application.
  \item These two values are then percent-encoded, concatenated and used as the
  key for an HMAC-SHA1 encoding of the base string \citep{TwitterHMACSHA}. The
  output from this encoding is now our signature.
\end{enumerate}

% In practice, we do the following \citep{TwitterAPISignature}. We start by using
% percent-encoding to encode: all the parameters, the request type, and the
% key-value pairs. Then we concatenate all the encoded strings. \\
% Following this, we concatenate two additional values which identify the
% requesting user and the application, namely the \textc{OAuth token secret} and
% the \textc{Consumer secret}. Here the Token Secret is unique to the user, and is
% given to us by Twitter when the user authenticates with our application. The
% Consumer Secret is a unique identifier for our application.\\
% These two values are then percent-encoded, concatenated, and used as a key for a
% HMAC-SHA1 encoding of the base string \citep{TwitterHMACSHA}. The output from
% this encoding is now our signature.
 
\subsection*{Signature method}
The signature method for Twitter is always \ac{HMAC-SHA1}. Any request without
this signature method is invalid. \ac{HMAC-SHA1} means that the cryptography
hash function used is \acused{SHA-1} \citep{TwitterHMACSHA}.

\subsection*{Timestamp}
The timestamp is a string created together with the request. The string is the
number of seconds since the Unix epoch, which is 1/1/1970. It is used to
determine when the request was made. If a request is marked as created before
the Unix epoch, it is invalid.

\subsection*{Authorization token}
The token is used to identify the user who is making the request; each user has
a unique token kept secret. This token can be received by submitting a users
login details with Twitter. As such, a user must be authorised before making
requests. In combination with the token, a user also has a Token Secret. This
secret is used when creating the signature.

% that the application is allowed to
% interact with the user's account. It is generated by Twitter by going to
% apps.twitter.com and clicking on the application 
% \fix{}{maybe go in-depth on how this is done}

\subsection*{Version}
The version always has to be 1.0 for the API to accept the request; this is
because the Twitter \ac{API} only uses OAuth 1.0, as opposed to OAuth 2.0.

\section{Creating the String}\label{label:stringCreate}
When all the necessary tokens have been generated, the authorization header
string itself can be created \citep{TwitterAPIAuth}. The finished header looks like this, where
\ldots\_val gets replaced with the corresponding token:\nl

OAuth oauth\_consumer\_key="oauth\_consumer\_key\_val",\\
oauth\_nonce="oauth\_nonce\_val", \\
oauth\_signature="oauth\_signature\_val", \\
oauth\_signature\_method="HMAC-SHA1", \\
oauth\_timestamp="oauth\_timestamp\_val", \\
oauth\_token="oauth\_token\_val", \\
oauth\_version="1.0" \\

This authorization header must then be supplied in the request to the Twitter
API whenever we make a request on behalf of the user.
