\textbf{Homepage:}
User is visibly confused and clicks different buttons on the keyboard since there is no clear indication of where to click on the screen.
-	The button should look more buttony
Check user page
User has no problem detecting what to do and quickly inserts the wanted username.
Authentication
When asked to insert her PIN, she asked what to do before clicking the correct button by herself
-	The button for finding the PIN could be an actual button instead that says “click here to get PIN”.
When presented with what features the application wants to be able to do, she does not like that it is able to post on her behalf. “I would never approve of this”
-	Reevaluate what the app asks permissions for. There is no reason for it to be able to post on the user’s behalf.
When presented with her PIN, she became much more confident and copied it into the correct text box, as well as providing her E-mail in the correct box.
While waiting for the result
When asked about the overall evaluation so far:
-	Confused about what it is about
	o	Should have been better at explaining the basics, what it is about, who it is
	    for and what to use the program for.
\textbf{E-mail}
Quickly identifies the button linking to the result and clicks it
-	Nothing wrong with the E-mail
Result screen
In general:
-	No clue what any of the graphs mean. It all seems overwhelming and confusing.
	o	Needs a lot of explaining text for each graph and what they show exactly. 
	o	Needs to tell that minus corresponds to left and plus corresponds to right.
	
When asked to find her own bias
-	Visibly confused
-	Scrolls up and down
-	Nervous laughter
-	Has no clue what to do
-	Fix:
	o	Much clearer indication that green means yourself
When asked to find the difference between BoW and Naïve Bayes, she does not even know which graphs this refers to.
-	The graphs need much better labels.
-	There needs to be a description in the top that explains that we have two approaches for determining bias and what they are.
	o	Jonathan had to explain these things before she could identify the graphs.
When asked to find the filterbubble of one of her friends (Donald Trump in the provided exercise) she looks around in panic and nervously laughs. Jonathan has to inform her to go back to the front page.
-	Could add a “Check another user” button or button leading back to the front page
\textbf{Result of friend}
When opening the second result, it confused her for a short second which page is which since the tabs are identical.
-	The checked username could be shown in the tab
When asked about how positive the friend’s filterbubble is, she is confused and has to have the word sentiment explained.
-	Fix: Could write an explanation on what sentiment means somewhere.
After the explanation, she is still uncertain what the graphs show.
-	The graph should have better labels to show that the x-axis is sentiment value and y is number of people in the filter bubble in the specific category.
-	The bars in the sentiment distribution bar graph could have other intervals, since no one is outside the range from -2 to 2 in this case.
Post test:
The test person felt stupid because she could not find out how to do any of the things.
-	This further indicates the severe need for better explanations and labels and overall more intuitive design. 

