\chapter{Problem Statement}\label{ch:problem}
Our project for this semester was how to break a filter bubble. Therefore, we
first approached it by trying to figure out which social media would be most
suitable and analyzed how to collect a vast amount of user data, from the sites
to identify a filter bubble.
This chapter will summarize the conclusions, and define a problem
statement.\nl

In \autoref{sec:social-media-conclusion} we concluded, that Twitter is most suitable
for gathering user data, as Twitter provide an \ac{API} that permits us to
easily request all relevant data from a user. This data can be requested from
any user, who has not set their account to private. The data consists of tweets,
followers, and friends for any such user.\nl

In \autoref{subsec:crawler} we discovered that there are restrictions to what
a crawler is allowed to access. We have determined that while it is possible to
use a regular crawler to gather data, it is preferable to use the official
Twitter \ac{API} designed for the purpose. We made this decision, as the
\ac{API} gives access to all relevant data by using a simple set of \ac{HTTP}
requests, while a crawler has to adhere to a stricter set of limitations.
However, we are still able to use the crawler architecture as a guideline for
how to design a solution.\nl

% In \autoref{emotions} we determined that we can identify a users filter bubble
% by how ``emotional'' they were about certain topics. This can be done by
% pairing key topical words like names of political figures, with emotional
% words like ``like", ``good", and ``hate".\nl

Based on these conclusions, we establish the following problem statement:

\begin{center}
\begin{minipage}{0.95\linewidth} 

\textbk{How can a software solution be developed as to permit a user to break
out of a filter bubble by using information gathered from social media. And how
can the developed software allow identify a user's filter bubble, and present
the user with information from outside of it?.}

\end{minipage}
\end{center}




