\section{Reading Guide}\label{sec:readingGuide}
This section is used to provide an overview of the report's content, and
provides a list of the various terms used throughout the report. 

\subsection{Chapter Guide}
\autoref{ch:intro} starts by briefly describing the project subject, namely  the
filter bubble. It ends by introducing a set of initial problems for further
analysis.\nl

\autoref{cha:DG} starts by discussing various social media sites which can act
as a source of useful user data, and how this data can be gathered and accessed.
It ends by concluding that Twitter is best suited for our needs, and that we
will use it as a data source.\nl

\autoref{cha:DA} starts by discussing how user data, in the form of tweets, can
be analyzed in order to determine a users filter bubble. In ends by concluding
that we want to make two models, one using a Bag-of-Words approach, and another
using a Naive Bayes Network.\nl

\autoref{ch:problem} follows on from the analysis of the problem area, and
states our intent to break the filter bubble by determining the political bias
of the people a user follows on Twitter.\nl

\autoref{cha:req} presents a number of functional- and usability requirements,
which are deemed necessary to fulfill in order to successfully develop the
software solution. We conclude that we want to build a web-application with a
webpage frontend.\nl

\autoref{ch:sysview} presents an overview of all parts of the developed system,
and describes how they interact with each other. The system consists of a
web-application front-end, a database, and a backend server.\nl

\autoref{cha:twitterAPI} describes how we interact with the Twitter API in order
to gather the required data for analysis.\nl

\autoref{DatabaseAPI} describes the development of the API which is used to
interacting with the database. This API is developed using the Laravel web
application framework.\nl

\autoref{queueAPI} describes the development of the API which is used to
interact with the backend server. This API is developed using the Microsoft
.NET framework in the C\# programming language.\nl

\autoref{workerLabel} describes the development of the Worker, which is the part
of the backend server responsible for determining a users filter bubble. This is
done using both the Bag-of-Words model, and the Naive Bayes Network.\nl

\autoref{cha:classification} describes the development of the two different
classification algorithms, namely the Bag-of-Words model, and the Naive Bayes
Network.\nl 

\autoref{GUI} presents the graphical user interface (GUI) of the web-application
front end. It also describes the design choices involved in developing the
visual presentation.\nl

\autoref{cha:usability} starts by presenting the usability testing of the
system. It then concludes on the quality of the system's frontend, and
determines a number of improvements to be implemented. Finally it presents the
improvements added based on the usability test.

\autoref{cha:testing} presents a number of tests which aim to ensure the quality
of the developed software solution. In ends by concluding the possible
bottlenecks in the execution process, namely the limited amounts of Tweets
retrievalble per second.\nl

\autoref{fwork} discusses what elements of the system are unfinished, or could
be subject for future development.\nl

\autoref{cha:disc} discusses the quality of the development process, and other
topics which requires reflection.\nl

\autoref{cha:conclusion} ends the report by concluding on the projects success in
relation to the system requirements determined in \autoref{cha:req}.









\subsection{Style List}
The following font styles are used throughout the report, and has the following meaning:

\begin{table}[H]
\centering
\begin{tabular}{|l|p{6cm}|}
\hline
\textbf{Style} & \textbf{Meaning} \\ \hline
\textc{Code} &  Code related elements e.g. libraries, methods, and classes.\\ \hline
\textbf{line x-y} & Line reference in code \\\hline
\end{tabular}
\caption{Notable font styles}
\end{table}


\subsection{Word List}
The following words are used throughout the report and has the following
meaning:

\begin{table}[H]
\centering
API
\begin{tabular}{|l|p{6cm}|}
\hline
\textbf{Word} & \textbf{Meaning} \\ \hline

\end{tabular}
\caption{Notable words}
\end{table}

\subsection{Code repositories}
The code base of the developed software solutions can be found in the following
repositories:

\begin{table}[H]
\centering
\begin{tabular}{|l|p{6cm}|}
\hline
\textbf{Project part} & \textbf{Url} \\ \hline
Worker \& Queue Server / \acs{API}  & \url{https://github.com/Crimix/BubbleBuster}.\\\hline 
Database \acs{API} / server & \url{https://github.com/Crimix/EnragedWindigo-DB}.\\\hline 
Front end & \url{https://github.com/Crimix/EnragedWindigo}.
\\\hline
\end{tabular}
\caption{Solution repositories}
\end{table}